Joint spatiotemporal models reveal dramatic shifts in mesopredator diel activity across individuals, habitat types and apex predator activity levels

### 2021-08-05 manuscript/manuscript.Rmd
removed model 2a

---
title: Joint spatiotemporal models reveal dynamic shifts in mesopredator spatial and diel activity for apex predator avoidance
author:
  - name: Matthew W. Rees
    email: matt.wayne.rees@gmail.com
    affiliation: UOM
    footnote: 1
  - name: Jack H. Pascoe
    email: 
    affiliation: CEC
  - name: Mark Le Pla
    email: 
    affiliation: CEC
  - name: Emma K. Birnbaum
    email: 
    affiliation: CEC
    footnote: 
  - name: Alan Robley
    email: 
    affiliation: ARI
  - name: Nick Golding
    email: 
    affiliation: CU,TKI
  - name: Brendan A. Wintle
    email: 
    affiliation: UOM
  - name: Bronwyn A. Hradsky
    email: 
    affiliation: UOM
    footnote: 
address:
  - code: UOM
    address: Quantitative & Applied Ecology Group, School of Ecosystem and Forest Science, The University of Melbourne, Parkville, VIC, Australia
  - code: CEC 
    address: Conservation Ecology Centre, Otway Lighthouse Rd, Cape Otway, VIC, Australia
  - code: ARI 
    address: Department of Environment, Land, Water and Planning, Arthur Rylah Institute for Environmental Research, Heidelberg, Australia
  - code: CU 
    address: Curtin University, Bentley, WA, Australia
  - code: TKI 
    address: Telethon Kids Institute, Perth Children's Hospital, Nedlands, WA, Australia
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  1. Background.
  2. Methods.
  3. Results.
  4. *Synthesis and applications.*

@@

>>>>

---
title: Joint spatiotemporal models reveal dramatic shifts in mesopredator diel activity across individuals, habitat types and apex predator activity levels
author:
  - name: Matthew W. Rees
    email: matt.wayne.rees@gmail.com
    affiliation: UOM
    footnote: 1
  - name: Jack H. Pascoe
    email: 
    affiliation: CEC
  - name: Mark Le Pla
    email: 
    affiliation: CEC
  - name: Emma K. Birnbaum
    email: 
    affiliation: CEC
    footnote: 
  - name: Alan Robley
    email: 
    affiliation: ARI
  - name: Nick Golding
    email: 
    affiliation: CU,TKI
  - name: Brendan A. Wintle
    email: 
    affiliation: UOM
  - name: Bronwyn A. Hradsky
    email: 
    affiliation: UOM
    footnote: 
address:
  - code: UOM
    address: Quantitative & Applied Ecology Group, School of Ecosystem and Forest Science, The University of Melbourne, Parkville, VIC, Australia
  - code: CEC 
    address: Conservation Ecology Centre, Otway Lighthouse Rd, Cape Otway, VIC, Australia
  - code: ARI 
    address: Department of Environment, Land, Water and Planning, Arthur Rylah Institute for Environmental Research, Heidelberg, Australia
  - code: CU 
    address: Curtin University, Bentley, WA, Australia
  - code: TKI 
    address: Telethon Kids Institute, Perth Children's Hospital, Nedlands, WA, Australia
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: |
  1. Background.
  2. Methods.
  3. Results.
  4. *Synthesis and applications.*

@@

```{r ind, out.width="100%", fig.cap = "Individual variations in feral cat diel activity patterns across the Glenelg region (A) and wet forests of the western Otway Ranges (B) in south-west Victoria, Australia. Dotted, vertical lines represent average sunrise and sunset times. Shaded areas indicate 95\\% confidence intervals."}
knitr::include_graphics("../figs/cat_ind.png")
```

### 2021-08-05 manuscript/manuscript.tex
removed model 2a

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1.1in]{geometry}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Joint spatiotemporal models reveal dynamic shifts in mesopredator spatial and diel activity for apex predator avoidance},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Joint spatiotemporal models reveal dynamic shifts in mesopredator spatial and diel activity for apex predator avoidance}
    \author[UOM]{Matthew W. Rees\corref{1}}
   \ead{matt.wayne.rees@gmail.com} 
    \author[CEC]{Jack H. Pascoe}

@@

On average, both predator species occupied similar times of the day. Lowest during the middle of the day, peaking during sunset and remaining relatively high at night and dawn.
Foxes had a stronger diel activity patterns than cats, much less likely to be out during the day.

@@

>>>>

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage[margin=1.1in]{geometry}
\bibliographystyle{elsarticle-harv}
\usepackage{longtable}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Joint spatiotemporal models reveal dramatic shifts in mesopredator diel activity across individuals, habitat types and apex predator activity levels},
            colorlinks=false,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

@@

  \title{Joint spatiotemporal models reveal dramatic shifts in mesopredator diel activity across individuals, habitat types and apex predator activity levels}
    \author[UOM]{Matthew W. Rees\corref{1}}
   \ead{matt.wayne.rees@gmail.com} 
    \author[CEC]{Jack H. Pascoe}

@@

On average, both predator species occupied similar times of the day--mostly nocturnal with activity peaks around sunrise and sunset. The main difference was that fox activity peaked just after sunset rather than on sunset. For foxes, this diel pattern was largely exhibited across all vegetation types except wet forest. In wet forests and rainforests, the hour of the day had little effect on foxes (especially considering diel activity curve here is being drawn towards a nocturnal pattern).

lowest activity during the middle of the day, peaking at sunrise and sunset times, while remaining relatively high at night and dawn.
Foxes had a stronger diel activity patterns than cats, much less likely to be out during the day.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/cat_ind} \caption{Individual variations in feral cat diel activity patterns across the Glenelg region (A) and wet forests of the western Otway Ranges (B) in south-west Victoria, Australia. Dotted, vertical lines represent average sunrise and sunset times. Shaded areas indicate 95\% confidence intervals.}\label{fig:ind}
\end{figure}
